### 2018-09-20 Latex/section_wave_cascade_f=0.tex
Start to include figures in the pdf file.
Rename and improve figures
Change width in Latex to equivalent in inches
Start making notebooks
Include figures in the article + add todo to README.rst

\begin{figure}
% \centerline{
% \includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
\caption{Spectral energy fluxes averaged over a long simulation for $c
= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
and plotted versus $k/k_f$.  }
\label{fig_seb}
\end{figure}

@@

\begin{figure}
% \centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
\caption{
Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo}) 
averaged over a long simulation for $c = 20$ and $n = 3840$.
%
The structure functions are normalized by $4 \eps r$.
%
Black thick line, $\mean{ \delta J_L|\delta \uu|^2 } 
+ c^2\mean{\delta u_L(\delta h)^2}$;
light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
%
The dotted straight line shows $4 \eps_q r$, 
where $\eps_q$ is the quadratic energy dissipation rate.
}
\label{fig_Kolmo}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
\caption{Spatio-temporal spectra of KE (dark lines) and APE (light
lines) for $c = 20$ and $n = 3840$ versus $\omega/\omega_l$, where
$\omega_l = c k$.  From the larger to the smaller spectra, $k/\delta k
= 12$, 27, 62, 143, 327, and 746.  }
\label{fig_spatiotemp_spectra}
\end{figure}

@@

\begin{figure}
% \centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
\caption{Compensated spectra
of total energy (thick black line)
kinetic energy (thin dark line) and
available potential energy (thin light line)
for $c = 40$ and $n = 7680$.}
\label{fig_spectra_c40}
\end{figure}

@@

\begin{figure}
\setlength{\halfwidth}{69mm}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c20}
% \hspace{-4mm}
% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c200}
% }
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c20}
% \hspace{-4mm}
% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c200}
% }
\caption{
Snapshots for $n = 1920$ and two values of the wave speed 
$c= 20$ (\textit{a,c}) and $c= 200$ (\textit{b,d}).
The colors represent the thickness in (\textit{a,b}) and
the $y$-component of the velocity in (\textit{c,d}).
The arrows represent the velocity field.
%
The coordinates are nondimensionalized by the characteristic scale of
the forcing $L_f = 3.57$.  }
\label{fig_phys}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
% }
\caption{
Ratio of the structure functions of the velocity increments 
$R_p(r) \equiv \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$
for $p = 2,$ 3 and 4.
The dotted straight lines indicate the values computed by the shock model:
$R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
%
The wave speed and the resolution are $c = 10$ and $n = 7680$.  }
\label{fig_ratio}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_flatness}
% }
\caption{ Flatness of the longitudinal and transverse increments for
$c = 10$ and $n = 7680$. The straight continuous lines indicate the
$r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
The inset shows the ratio $F_T/F_L$ and the corresponding value
computed by the shock model, $F_T/F_L = 1.5$.  }
\label{fig_flatness}
\end{figure}
%
Figure~\ref{fig_flatness} shows the flatness of the longitudinal and
transverse increments, computed from a numerical simulation for $c =
10$ and $n = 7680$.
%
For a Gaussian probability distribution the flatness factor is equal
to 3 whereas the shock model predict flatness factors scaling like
$r^{-1}$.
%
We see that here the flatness factors are much larger than 3, of the
order of $10^3$.
%
Remarkably, they scale approximately as $r^{-1}$ as predicted by the
shock model and the ratio $F_T/F_L$ is very close to the predicted
value 1.5.

>>>>

\begin{figure}
\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_spect_energy_budg_c=100_N=3840}}
\caption{Spectral energy fluxes averaged over a long simulation for $c
= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
and plotted versus $k/k_f$.  }
\label{fig_seb}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_Kolmo_c=20_N=3840}}
\caption{
Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo})
averaged over a long simulation for $c = 20$ and $n = 3840$.
%
The structure functions are normalized by $4 \eps r$.
%
Black thick line, $\mean{ \delta J_L|\delta \uu|^2 }
+ c^2\mean{\delta u_L(\delta h)^2}$;
light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
%
The dotted straight line shows $4 \eps_q r$,
where $\eps_q$ is the quadratic energy dissipation rate.
}
\label{fig_Kolmo}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=3.15in]{../Old/Figs/fig_spatiotempspectra_c20_Nh3840}}
\caption{Spatio-temporal spectra of KE (dark lines) and APE (light
lines) for $c = 20$ and $n = 3840$ versus $\omega/\omega_l$, where
$\omega_l = c k$.  From the larger to the smaller spectra, $k/\delta k
= 12$, 27, 62, 143, 327, and 746.  }
\label{fig_spatiotemp_spectra}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=8cm]{../Pyfig/fig_spectra_c=100_nh=7680}}
\caption{Compensated spectra
of total energy (thick black line)
kinetic energy (thin dark line) and
available potential energy (thin light line)
for $c = 40$ and $n = 7680$.}
\label{fig_spectra_c40}
\end{figure}

@@

\begin{figure}
% \setlength{\halfwidth}{2.72in}
\centerline{\includegraphics[width=5.20in]{../Pyfig/fig_phys_fields_wave}}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c20}
% \hspace{-4mm}
% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c200}
% }
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c20}
% \hspace{-4mm}
% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c200}
% }
\caption{
Snapshots for $n = 1920$ and two values of the wave speed
$c= 20$ (\textit{a,c}) and $c= 200$ (\textit{b,d}).
The colors represent the thickness in (\textit{a,b}) and
the $y$-component of the velocity in (\textit{c,d}).
The arrows represent the velocity field.
%
The coordinates are nondimensionalized by the characteristic scale of
the forcing $L_f = 3.57$.  }
\label{fig_phys}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=\halfwidth]{../Pyfig/fig_ratio_strfct}}
\caption{
Ratio of the structure functions of the velocity increments
$R_p(r) \equiv \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$
for $p = 2,$ 3 and 4.
The dotted straight lines indicate the values computed by the shock model:
$R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
%
The wave speed and the resolution are $c = 10$ and $n = 7680$.  }
\label{fig_ratio}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=5.12in]{../Pyfig/fig_flatness}}
\caption{ Flatness of the longitudinal and transverse increments for
$c = 10$ and $n = 7680$. The straight continuous lines indicate the
$r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
The inset shows the ratio $F_T/F_L$ and the corresponding value
computed by the shock model, $F_T/F_L = 1.5$.  }
\label{fig_flatness}
\end{figure}
%
Figure~\ref{fig_flatness} shows the flatness of the longitudinal and
transverse increments, computed from a numerical simulation for $c =
10$ and $n = 7680$.
%
For a Gaussian probability distribution the flatness factor is equal
to 3 whereas the shock model predict flatness factors scaling like
$r^{-1}$.
%
We see that here the flatness factors are much larger than 3, of the
order of $10^3$.
%
Remarkably, they scale approximately as $r^{-1}$ as predicted by the
shock model and the ratio $F_T/F_L$ is very close to the predicted
value 1.5.
